Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-13 kappa.tex
Enhance snapshots plot.
Add list of papers.

% Base class and packages
\documentclass{article}
\usepackage{amsmath}
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage[onehalfspacing]{setspace}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{doi}  % needs to be loaded after hyperref
\usepackage{graphicx}
\graphicspath{{figures/}}

@@

% Document properties
\title{Numerical simulation of the Cordilleran ice sheet \\
       through the last glacial cycle}
\author{Julien Seguinot}

@@

\maketitle
\tableofcontents

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-snapshots}}
  \caption{\textbf{(a)} Modelled growth and decay of the last Cordilleran ice
           sheet. Basal topography surface topography (1\,km contours) and
           surface velocity (m/a).
           \textbf{(b)} Evolution of total ice volume during the entire last
           glacial cycle, expressed as meters of sea-level equivalent. The
           simulation uses a horizontal resolution of 6\,km and is forced by
           atmospheric fields from the NARR \citep{Mesinger.etal.2006} and
           temperature offset time-series derived from the GRIP
           \citep{Dansgaard.etal.1993} ice-core record as described in \CCYC.
           \todo{X-tick snapshot times on time series plot and thicken the
                 vertical lines. Add (a) and (b) subfigure labels. Link lower
                 and upper panels; see recipe at
                 \url{http://stackoverflow.com/questions/17543359/}.}}
  \label{fig:plot-snapshots}
\end{figure}

>>>>

% Base class and packages
\documentclass{article}
%\makeatletter\newcommand{\@ptsize}{0}\makeatother  % needed by setspace
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{doi}  % needs to be loaded after hyperref
\usepackage{graphicx}
\onehalfspacing
\graphicspath{{figures/}}
\nobibliography*

@@

% Document properties
\title{Numerical simulation of the Cordilleran ice sheet \\
       through the last glacial cycle}
%\runningtitle{Numerical modelling of the Cordilleran ice sheet}
\author{Julien Seguinot}

@@

\section*{List of papers}

This doctoral dissertation consists of a cover summary and the following
papers, which are referred to by their Roman numerals in the text.

\begin{description}
  \item[\CCLI] \bibentry{Seguinot.etal.2014}
  \item[\PSDV] \bibentry{Seguinot.2013}
  \item[\PSDP] \bibentry{Seguinot.Rogozhina.2014}
  \item[\CCYC] \bibentry{Seguinot.etal.inpreparation}
\end{description}

\vfill
\noindent\textbf{Author contributions}

\small{\begin{enumerate}
  \item[I] I set-up the ice sheet model and supercomputing workflow, ran the
simulations and wrote the manuscript; C.~Khroulev implemented necessary code
changes in PISM; I.~Rogozhina guided experiment design; A.~P.~Stroeven
initiated the Cordilleran ice sheet modelling project; and Q.~Zhang prepared
some of the forcing data. All authors contributed to improve the text.
  \item[II] I analysed the weather data, wrote the positive degree day model,
ran computations and wrote the manuscript. I.~Rogozhina helped to assess the
reviews.
  \item[III] I analysed the weather data; I.~Rogozhina and I wrote the manuscript.
  \item[IV] I implemented necessary code changes in PISM, ran the simulations
and wrote the manuscript; I.~Rogozhina guided experiment design; M.~Margold,
J.~Kleman and A.~P.~Stroeven took part in the interpretation. All authors
contributed to improve the text.
\end{enumerate}}

\newpage
\maketitle
\tableofcontents
\newpage

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-snapshots}}
  \caption{\textbf{(a)} Modelled growth and decay of the last Cordilleran ice
           sheet. Basal topography surface topography (1\,km contours) and
           surface velocity (m/a).
           \textbf{(b)} Evolution of total ice volume during the entire last
           glacial cycle, expressed as meters of sea-level equivalent. The
           simulation uses a horizontal resolution of 6\,km and is forced by
           atmospheric fields from the NARR \citep{Mesinger.etal.2006} and
           temperature offset time-series derived from the GRIP
           \citep{Dansgaard.etal.1993} ice-core record as described in \CCYC.}
  \label{fig:plot-snapshots}
\end{figure}
